Quantum Interval-Valued Probability: Measurement and Probability

### 2017-09-10 prop_iop.tex
prop_iop.tex \subsection{Classical and Quantum Probability Measures} Updating a deinition...

\begin{definition}\label{def:sub-event-space}Given a Hilbert space
$\Hilb$, $\events'\subseteq\events$ is called a sub-event space
if it satisfies the follow conditions.
\begin{itemize}
\item $\mathbb{0}\in\events'$.
\item $\mathbb{1}\in\events'$.
\item For any projection $P\in\events'$, we have $\mathbb{1}-P\in\events'$.
\item For a set of mutually orthogonal projections $\left\{ P_{i}\right\} _{i=1}^{N}\subseteq\events'$,
we have $\sum_{i=1}^{N}P_{i}\in\events'$.
\end{itemize}
By replacing every occurrence of $\events$ by $\events'$ in definition~\ref{def:QuantumCryptodeterministicMeasures},
\ref{def:QuantumProbabilitySpace}, and \ref{def:QuantumInterval-valuedProbability},
it is straightforward to define a quantum cryptodeterministic, real-valued
probability, and interval-valued probability measure on $\events'$.\end{definition}

\begin{thm}\label{thm:sub-event-space}Given a Hilbert space~$\Hilb$
and a mutually commuting sub-event space~$\events'\subseteq\events$,
there is a set~$\Omega$, another commuting sub-event space~$\widehat{\events}$
with $\events'\subseteq\widehat{\events}\subseteq\events$, and a
bijection~$\tau:\widehat{\events}\rightarrow2^{\Omega}$ such that:
\begin{enumerate}
\item \label{enu:sub-event-space-real-quantum2classical}If $\mu':\events'\rightarrow\left[0,1\right]$
is a quantum real-valued probability measure, then there is a classical
real-valued probability measure\nb$\mu:2^{\Omega}\rightarrow\left[0,1\right]$
such that $\mu'\left(P\right)=\mu\left(\tau\left(P\right)\right)$
for all $P\in\events'$.
\item \label{enu:sub-event-space-interval-quantum2classical}If $\bar{\mu}':\events'\rightarrow\mathscr{I}$
is a quantum interval-valued probability measure, then there is a
classical interval-valued probability measure\nb$\bar{\mu}:2^{\Omega}\rightarrow\mathscr{I}$
such that $\bar{\mu}'\left(P\right)=\bar{\mu}\left(\tau\left(P\right)\right)$
for all $P\in\events'$.
\item \label{enu:sub-event-space-real-classical2quantum}If $\mu:2^{\Omega}\rightarrow\left[0,1\right]$
is a classical real-valued probability measure, then $\mu\circ\tau:\widehat{\events}\rightarrow\left[0,1\right]$
is a QRVPM.
\item \label{enu:sub-event-space-Gleason}Given a QRVPM\nb$\widehat{\mu}:\widehat{\events}\rightarrow\left[0,1\right]$,
there is a density matrix~$\rho$ such that $\mu_{\rho}^{\mathrm{B}}\left(P\right)=\widehat{\mu}\left(P\right)$
for all $P\in\widehat{\events}$.
\item $\rho$ in the previous case may not be unique.
\item The bijection~$\tau:\widehat{\events}\rightarrow2^{\Omega}$ preserves
the following operations.
\begin{itemize}
\item $\tau\left(\mathbb{0}\right)=\emptyset$.
\item $\tau\left(\mathbb{1}\right)=\Omega$.
\item For any projection $P\in\widehat{\events}$, we have $\tau\left(\mathbb{1}-P\right)=\Omega-\tau\left(P\right)$.
\item For a set of mutually orthogonal projections $\left\{ P_{i}\right\} _{i=1}^{N}\subseteq\widehat{\events}$,
we have $\tau\left(\sum_{i=1}^{N}P_{i}\right)=\sum_{i=1}^{N}\tau\left(P_{i}\right)$.
\end{itemize}
\end{enumerate}
\end{thm}

@@

\begin{definition}Given an observable~$\mathbf{O}$ with its spectral
decomposition~(\ref{eq:spectrum-decomposition}). A sub-event space~$\events'\subseteq\events$
is called a sub-event space induced by $\mathbf{O}$ if it is the
minimal sub-event space satisfying $\left\{ P_{i}^{-}\right\} _{i=1}^{N^{-}}\cup\left\{ P_{i}^{+}\right\} _{i=1}^{N^{+}}\subseteq\events'$.\end{definition}

>>>>

\begin{definition}\label{def:sub-event-space}Given a Hilbert space
$\Hilb$, a set of event~$\events'\subseteq\events$ is called a
subspace if it satisfies the follow conditions.
\begin{itemize}
\item $\mathbb{0}\in\events'$.
\item $\mathbb{1}\in\events'$.
\item For any projection $P\in\events'$, we have $\mathbb{1}-P\in\events'$.
\item For a set of mutually orthogonal projections $\left\{ P_{i}\right\} _{i=1}^{N}\subseteq\events'$,
we have $\sum_{i=1}^{N}P_{i}\in\events'$.
\end{itemize}
By replacing every occurrence of $\events$ by $\events'$ in definition~\ref{def:QuantumCryptodeterministicMeasures},
\ref{def:QuantumProbabilitySpace}, and \ref{def:QuantumInterval-valuedProbability},
it is straightforward to define a quantum cryptodeterministic, real-valued
probability, and interval-valued probability measure on $\events'$.{
Also, }$\events'$ is called convex if we have $P_{1}P_{2}\in\events'$
for a pair of mutually commuting projections $P_{1}$ and $P_{2}\in\events'$.\end{definition}

\begin{thm}\label{thm:sub-event-space}Given a Hilbert space~$\Hilb$
and a mutually commuting sub-event space~$\events'\subseteq\events$,
there is a set~$\Omega$, another commuting sub-event space~$\widehat{\events}$
with $\events'\subseteq\widehat{\events}\subseteq\events$, and a
bijection~$\tau:\widehat{\events}\rightarrow2^{\Omega}$ such that:
\begin{enumerate}
\item \label{enu:sub-event-space-real-quantum2classical}If $\mu':\events'\rightarrow\left[0,1\right]$
is a quantum real-valued probability measure, then there is a classical
real-valued probability measure\nb$\mu:2^{\Omega}\rightarrow\left[0,1\right]$
such that $\mu'\left(P\right)=\mu\left(\tau\left(P\right)\right)$
for all $P\in\events'$.
\item \label{enu:sub-event-space-interval-quantum2classical}If $\bar{\mu}':\events'\rightarrow\mathscr{I}$
is a quantum interval-valued probability measure, then there is a
classical interval-valued probability measure\nb$\bar{\mu}:2^{\Omega}\rightarrow\mathscr{I}$
such that $\bar{\mu}'\left(P\right)=\bar{\mu}\left(\tau\left(P\right)\right)$
for all $P\in\events'$.
\item \label{enu:sub-event-space-real-classical2quantum}If $\mu:2^{\Omega}\rightarrow\left[0,1\right]$
is a classical real-valued probability measure, then $\mu\circ\tau:\widehat{\events}\rightarrow\left[0,1\right]$
is a QRVPM.
\item \label{enu:sub-event-space-Gleason}Given a QRVPM\nb$\widehat{\mu}:\widehat{\events}\rightarrow\left[0,1\right]$,
there is a density matrix~$\rho$ such that $\mu_{\rho}^{\mathrm{B}}\left(P\right)=\widehat{\mu}\left(P\right)$
for all $P\in\widehat{\events}$.
\item $\rho$ in the previous case may not be unique.
\item The bijection~$\tau:\widehat{\events}\rightarrow2^{\Omega}$ preserves
the following operations.
\begin{itemize}
\item $\tau\left(\mathbb{0}\right)=\emptyset$.
\item $\tau\left(\mathbb{1}\right)=\Omega$.
\item For any projection $P\in\widehat{\events}$, we have $\tau\left(\mathbb{1}-P\right)=\Omega\backslash\tau\left(P\right)$.
\item For a set of mutually orthogonal projections $\left\{ P_{i}\right\} _{i=1}^{N}\subseteq\widehat{\events}$,
we have $\tau\left(\sum_{i=1}^{N}P_{i}\right)=\bigcup_{i=1}^{N}\tau\left(P_{i}\right)$.
\item For a pair of mutually commuting projections $P_{1}$ and $P_{2}\in\events'$,
we have $\tau\left(P_{1}P_{2}\right)=\tau\left(P_{1}\right)\cap\tau\left(P_{2}\right)$.
\end{itemize}
\end{enumerate}
\end{thm}

@@

\begin{definition}Given an observable~$\mathbf{O}$ with its spectral
decomposition~(\ref{eq:spectrum-decomposition}). A subspace of events~$\events'\subseteq\events$
is called a subspace of events induced by $\mathbf{O}$ if it is the
minimal subspace of events satisfying $\left\{ P_{i}^{-}\right\} _{i=1}^{N^{-}}\cup\left\{ P_{i}^{+}\right\} _{i=1}^{N^{+}}\subseteq\events'$.
Obvious, $\events'$ is convex.\end{definition}
